---
title: "Physical environmental (i.e. geospatial) DataSchema"
output: html_document
---
# Table of Contents
1. [Natural environment - Urban Atlas subdomain] #(Natural-environment - Urban-Atlas-subdomain)  
2. [Natural environment - CORINE subdomain] #(Natural-environment - CORINE-subdomain)  
3. [Built environment - Urban Atlas subdomain] #(Built-environment - Urban-Atlas-subdomain)  
4. [Built environment - CORINE subdomain] #(Built-environment - CORINE-subdomain)  
5. [Land use - Urban Atlas subdomain] #(Land-use - Urban-Atla-subdomain)  
6. [Land use - CORINE subdomain] #(Land-use - CORINE-subdomain)  
7. [Built environment - Urban Atlas subdomain] #(Built-environment - Urban-Atlas-subdomain)  

# Natural environment - Urban Atlas  

### **Variable label**: Distance to green urban areas in 2006 (Urban Atlas)   
**Variable name**: physenv_ua_ne_greenurban_06  
**Variable description**: Absolute distance to the nearest polygon marked as green urban area in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Distance to green urban areas in 2012 (Urban Atlas)
**Variable name**: physenv_ua_ne_greenurban_12  
**Variable description**: Absolute distance to the nearest polygon marked as green urban area in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Distance to forests in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_ne_forests_06  
**Variable description**: Absolute distance to the nearest polygon marked as forest in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Distance to forests in 2012 (Urban Atlas)   
**Variable name**: physenv_ua_ne_forests_12
**Variable description**: Absolute distance to the nearest polygon marked as forest in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Distance to blue spaces in 2006 (Urban Atlas)    
**Variable name**: physenv_ua_ne_bluespace_06  
**Variable description**: Absolute distance to the nearest polygon marked as water in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: - 

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Distance to blue spaces in 2012 (Urban Atlas)    
**Variable name**: physenv_ua_ne_bluespace_12  
**Variable description**: Absolute distance to the nearest polygon marked as water in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: - 

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Distance to agricultural land in 2006 (Urban Atlas)    
**Variable name**: physenv_ua_ne_agriland_06  
**Variable description**: Absolute distance to the nearest polygon. No distinction is made between different types of agricultural land in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: - 

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Distance to agricultural land in 2012 (Urban Atlas)    
**Variable name**: physenv_ua_ne_agriland_12  
**Variable description**: Absolute distance to the nearest polygon. No distinction is made between different types of agricultural land in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: - 

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Distance to total green spaces in 2006 (Urban Atlas)   
**Variable name**: physenv_ua_ne_totalgreen_06  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of green spaces (forests + green urban  areas) in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Distance to total green spaces in 2012 (Urban Atlas)   
**Variable name**: physenv_ua_ne_totalgreen_12  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of green spaces (forests + green urban  areas) in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Distance to total blue spaces in 2006 (Urban Atlas)   
**Variable name**: physenv_ua_ne_totalblue_06  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of blue spaces (water + wetlands) in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Distance to total blue spaces in 2012 (Urban Atlas)   
**Variable name**: physenv_ua_ne_totalblue_12  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of blue spaces (water + wetlands) in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Distance to total blue and green Spaces in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_ne_totalbluegreen_06  
**Variable description**: Absolute distance to the nearest polygon. Total of both green and blue space totals in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Distance to total blue and green Spaces in 2012 (Urban Atlas)   
**Variable name**: physenv_ua_ne_totalbluegreen_12  
**Variable description**: Absolute distance to the nearest polygon. Total of both green and blue space totals in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of green urban areas in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_ne_greenurban_area_06  
**Variable description**: Area size of the nearest polygon marked as green urban area in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of green urban areas in 2012 (Urban Atlas)   
**Variable name**: physenv_ua_ne_greenurban_area_12  
**Variable description**: Area size of the nearest polygon marked as green urban area in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of Forests in 2006 (Urban Atlas)   
**Variable name**: physenv_ua_ne_forests_area_06  
**Variable description**: Area size of the nearest polygon marked as forest in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of Forests in 2012 (Urban Atlas)    
**Variable name**: physenv_ua_ne_forests_area_12   
**Variable description**: Area size of the nearest polygon marked as forest in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size blue spaces area size in 2006 (Urban Atlas)   
**Variable name**: physenv_ua_ne_bluespace_area_06  
**Variable description**: Area size of the nearest polygon marked as water in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size blue spaces area size in 2012 (Urban Atlas)   
**Variable name**: physenv_ua_ne_bluespace_area_12  
**Variable description**: Area size of the nearest polygon marked as water in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size agricultural land in 2006 (Urban Atlas)   
**Variable name**: physenv_ua_ne_agriland_area_06  
**Variable description**: Area size of the nearest polygon. No distinction is made between different types of agricultural land in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size agricultural land in 2012 (Urban Atlas)   
**Variable name**: physenv_ua_ne_agriland_area_12  
**Variable description**: Area size of the nearest polygon. No distinction is made between different types of agricultural land in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size total green spaces in 2006 (Urban Atlas)   
**Variable name**: physenv_ua_ne_totalgreen_area_06  
**Variable description**: Area size of the nearest polygon. Total of all categories of green spaces (forests + green urban areas) in 2006 from Urban Atalas data.  
**Variable type**: decimal   
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size total green spaces in 2012 (Urban Atlas)   
**Variable name**: physenv_ua_ne_totalgreen_area_12  
**Variable description**: Area size of the nearest polygon. Total of all categories of green spaces (forests + green urban areas) in 2012 from Urban Atalas data.  
**Variable type**: decimal   
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size total blue spaces in 2006 (Urban Atlas)   
**Variable name**: physenv_ua_ne_totalblue_area_06  
**Variable description**: Area size of the nearest polygon. Total of all categories of blue spaces (water + wetlands) in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size total blue spaces in 2012 (Urban Atlas)   
**Variable name**: physenv_ua_ne_totalblue_area_12  
**Variable description**: Area size of the nearest polygon. Total of all categories of blue spaces (water + wetlands) in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size total blue and green Spaces in 2006 (Urban Atlas)   
**Variable name**: physenv_ua_ne_totalbluegreen_area_06  
**Variable description**: Area size of the nearest polygon. Total of both green and blue space totals in 2006 from Urban Atalas data.    
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size total blue and green Spaces in 2012 (Urban Atlas)   
**Variable name**: physenv_ua_ne_totalbluegreen_area_12  
**Variable description**: Area size of the nearest polygon. Total of both green and blue space totals in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green urban areas within 100 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_greenurban100_06  
**Variable description**: Total amount of m2 of green urban areas within 100 meter buffer in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green urban areas within 100 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_greenurban100_06  
**Variable description**: Total amount of m2 of green urban areas within 100 meter buffer in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of forests within 100 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_forests100_06  
**Variable description**: Total amount of m2 of forests within 100 meter buffer in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of forests within 100 meter buffer in 2012 (Urban Atlas)  
**Variable name**: Total amount of m2 of forests within 100 meter buffer in 2012 from Urban Atalas data.  
**Variable description**: physenv_ua_bf_forests100_12   
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue space within 100 meter buffer in 2006 (Uban Atlas)  
**Variable name**: physenv_ua_bf_bluespace100_06  
**Variable description**: Total amount of m2 of blue space within 100 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue space within 100 meter buffer in 2012 (Uban Atlas)  
**Variable name**: physenv_ua_bf_bluespace100_12  
**Variable description**: Total amount of m2 of blue space within 100 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of agricultural land within 100 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_agriland100_06  
**Variable description**: Total amount of m2 of agricultural land within 100 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of agricultural land within 100 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_agriland100_12  
**Variable description**: Total amount of m2 of agricultural land within 100 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total green space within 100 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalgreen100_06  
**Variable description**: Total amount of m2 of green spaces within 100 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total green space within 100 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalgreen100_12  
**Variable description**: Total amount of m2 of green spaces within 100 meter buffer in 2012 Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue space within 100 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalblue100_06  
**Variable description**: Total amount of m2 of blue spaces within 100 meter buffer in 2006 from Urban Atlas data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue space within 100 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalblue100_12  
**Variable description**: Total amount of m2 of blue spaces within 100 meter buffer in 2012 from Urban Atlas data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue and green space within 100 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalbluegreen100_06  
**Variable description**: Total amount of m2 of blue and green spaces within 100 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue and green space within 100 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalbluegreen100_12  
**Variable description**: Total amount of m2 of blue and green spaces within 100 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Green urban areas within 100 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban100_90  
**Variable description**: Total amount of m2 of green urban areas within 100 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Green urban areas within 100 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban100_00  
**Variable description**: Total amount of m2 of green urban areas within 100 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Green urban areas within 100 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban100_06  
**Variable description**: Total amount of m2 of green urban areas within 100 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Green urban areas within 100 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban100_12  
**Variable description**: Total amount of m2 of green urban areas within 100 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Forests within 100 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_forests100_90  
**Variable description**: Total amount of m2 of forests within 100 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Forests within 100 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_forests100_00  
**Variable description**: Total amount of m2 of forests within 100 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Forests within 100 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_forests100_06  
**Variable description**: Total amount of m2 of forests within 100 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Forests within 100 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_forests100_12  
**Variable description**: Total amount of m2 of forests within 100 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Blue spaces within 100 meter buffer 1990 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace100_90  
**Variable description**: Total amount of m2 of blue space within 100 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Blue spaces within 100 meter buffer 2000 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace100_00  
**Variable description**: Total amount of m2 of blue space within 100 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Blue spaces within 100 meter buffer 2006 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace100_06  
**Variable description**: Total amount of m2 of blue space within 100 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Blue spaces within 100 meter buffer 2012 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace100_12  
**Variable description**: Total amount of m2 of blue space within 100 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Agricultural land within 100 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_agriland100_90  
**Variable description**: Total amount of m2 of agricultural land within 100 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Agricultural land within 100 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_agriland100_00  
**Variable description**: Total amount of m2 of agricultural land within 100 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Agricultural land within 100 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_agriland100_06  
**Variable description**: Total amount of m2 of agricultural land within 100 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Agricultural land within 100 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_agriland100_12  
**Variable description**: Total amount of m2 of agricultural land within 100 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total green space within 100 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_totalgreen100_90  
**Variable description**: Total amount of m2 of green spaces within 100 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total green space within 100 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_totalgreen100_00  
**Variable description**: Total amount of m2 of green spaces within 100 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total green space within 100 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_totalgreen100_06  
**Variable description**: Total amount of m2 of green spaces within 100 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total green space within 100 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_totalgreen100_12  
**Variable description**: Total amount of m2 of green spaces within 100 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue space within 100 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue100_09  
**Variable description**: Total amount of m2 of blue spaces within 100 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue space within 100 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue100_00  
**Variable description**: Total amount of m2 of blue spaces within 100 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue space within 100 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue100_06  
**Variable description**: Total amount of m2 of blue spaces within 100 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue space within 100 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue100_12  
**Variable description**: Total amount of m2 of blue spaces within 100 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue and green space within 100 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_totalbluegreen100_90  
**Variable description**: Total amount of m2 of blue and green spaces within 100 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue and green space within 100 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_totalbluegreen100_00  
**Variable description**: Total amount of m2 of blue and green spaces within 100 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue and green space within 100 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_totalbluegreen100_06  
**Variable description**: Total amount of m2 of blue and green spaces within 100 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total blue and green space within 100 meter buffer in 2012 (CORINE) 
**Variable name**: physenv_cn_bf_totalbluegreen100_12  
**Variable description**: Total amount of m2 of blue and green spaces within 100 meter buffer in 2012 from CORINE data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green urban areas within 400 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_greenurban400_06  
**Variable description**: Total amount of m2 of green urban areas within 400 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green urban areas within 400 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_greenurban400_12  
**Variable description**: Total amount of m2 of green urban areas within 400 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of forests within 400 meter buffer in 2006 (Urban Atlas)
**Variable name**: physenv_ua_bf_forests400_06  
**Variable description**: Total amount of m2 of forests within 400 meter buffer in 2006 from Urban Atlas data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of forests within 400 meter buffer in 2012 (Urban Atlas)
**Variable name**: physenv_ua_bf_forests400_12  
**Variable description**: Total amount of m2 of forests within 400 meter buffer in 2012 from Urban Atlas data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue space within 400 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_bluespace400_06  
**Variable description**: Total amount of m2 of blue space within 400 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue space within 400 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_bluespace400_12  
**Variable description**: Total amount of m2 of blue space within 400 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of agricultural land within 400 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_agriland400_06  
**Variable description**: Total amount of m2 of agricultural land within 400 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of agricultural land within 400 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_agriland400_12  
**Variable description**: Total amount of m2 of agricultural land within 400 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: 
**Variable name**: 
**Variable description**: 
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of green spaces within 400 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalgreen400_06  
**Variable description**: Total amount of m2 of green spaces within 400 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal   
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of green spaces within 400 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalgreen400_12  
**Variable description**: Total amount of m2 of green spaces within 400 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue spaces within 400 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalblue400_06  
**Variable description**: Total amount of m2 of blue spaces within 400 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue spaces within 400 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalblue400_12  
**Variable description**: Total amount of m2 of blue spaces within 400 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```    


### **Variable label**: Total amount of m2 of blue and green spaces within 400 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalbluegreen400_06  
**Variable description**: Total amount of m2 of blue and green spaces within 400 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue and green spaces within 400 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalbluegreen400_12  
**Variable description**: Total amount of m2 of blue and green spaces within 400 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of green urban areas within 400 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban400_90  
**Variable description**: Total amount of m2 of green urban areas within 400 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of green urban areas within 400 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban400_00  
**Variable description**: Total amount of m2 of green urban areas within 400 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```    


### **Variable label**: Total amount of m2 of green urban areas within 400 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban400_06  
**Variable description**: Total amount of m2 of green urban areas within 400 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of green urban areas within 400 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban400_12  
**Variable description**: Total amount of m2 of green urban areas within 400 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```    


### **Variable label**: Total amount of m2 of forest within 400 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_forests400_90  
**Variable description**:  Total amount of m2 of forests within 400 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of forest within 400 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_forests400_00  
**Variable description**:  Total amount of m2 of forests within 400 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of forest within 400 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_forests400_06  
**Variable description**:  Total amount of m2 of forests within 400 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of forest within 400 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_forests400_12  
**Variable description**:  Total amount of m2 of forests within 400 meter buffer in  from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue space within 400 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace400_90  
**Variable description**: Total amount of m2 of blue space within 400 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue space within 400 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace400_00  
**Variable description**: Total amount of m2 of blue space within 400 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue space within 400 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace400_06  
**Variable description**: Total amount of m2 of blue space within 400 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue space within 400 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace400_12  
**Variable description**: Total amount of m2 of blue space within 400 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of agricultural land within 400 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_agriland400_90  
**Variable description**:  Total amount of m2 of agricultural land within 400 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of agricultural land within 400 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_agriland400_00  
**Variable description**:  Total amount of m2 of agricultural land within 400 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of agricultural land within 400 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_agriland400_06  
**Variable description**:  Total amount of m2 of agricultural land within 400 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of agricultural land within 400 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_agriland400_12  
**Variable description**:  Total amount of m2 of agricultural land within 400 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of green spaces within 400 meter buffer in 1990 (CORINE)
**Variable name**: physenv_cn_bf_totalgreen400_90
**Variable description**: Total amount of m2 of green spaces within 400 meter buffer in 1990 from CORINE data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of green spaces within 400 meter buffer in 2000 (CORINE)
**Variable name**: physenv_cn_bf_totalgreen400_00
**Variable description**: Total amount of m2 of green spaces within 400 meter buffer in 2000 from CORINE data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of green spaces within 400 meter buffer in 2006 (CORINE)
**Variable name**: physenv_cn_bf_totalgreen400_06
**Variable description**: Total amount of m2 of green spaces within 400 meter buffer in 2006 from CORINE data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of green spaces within 400 meter buffer in 2012 (CORINE)
**Variable name**: physenv_cn_bf_totalgreen400_12
**Variable description**: Total amount of m2 of green spaces within 400 meter buffer in 2012 from CORINE data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue spaces within 400 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue400_90  
**Variable description**: Total amount of m2 of blue spaces within 400 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   

### **Variable label**: Total amount of m2 of blue spaces within 400 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue400_00  
**Variable description**: Total amount of m2 of blue spaces within 400 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue spaces within 400 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue400_06  
**Variable description**: Total amount of m2 of blue spaces within 400 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue spaces within 400 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue400_12  
**Variable description**: Total amount of m2 of blue spaces within 400 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue and green spaces within 400 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_totalbluegreen400_90  
**Variable description**:  Total amount of m2 of blue and green spaces within 400 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue and green spaces within 400 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_totalbluegreen400_00  
**Variable description**:  Total amount of m2 of blue and green spaces within 400 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue and green spaces within 400 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_totalbluegreen400_06  
**Variable description**:  Total amount of m2 of blue and green spaces within 400 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of blue and green spaces within 400 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_totalbluegreen400_12  
**Variable description**:  Total amount of m2 of blue and green spaces within 400 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```    


### **Variable label**: Total amount of m2 of sports & leisure facilities within 400 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_facilities400_06  
**Variable description**:  Total amount of m2 of sports & leisure facilities within 400 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of sports & leisure facilities within 400 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_facilities400_12  
**Variable description**:  Total amount of m2 of sports & leisure facilities within 400 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of sports & leisure facilities within 400 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_facilities400_90  
**Variable description**: Total amount of m2 of sports & leisure facilities within 400 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of sports & leisure facilities within 400 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_facilities400_00  
**Variable description**: Total amount of m2 of sports & leisure facilities within 400 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of sports & leisure facilities within 400 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_facilities400_06  
**Variable description**: Total amount of m2 of sports & leisure facilities within 400 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of sports & leisure facilities within 400 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_facilities400_12  
**Variable description**: Total amount of m2 of sports & leisure facilities within 400 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```   


### **Variable label**: Total amount of m2 of green urban areas within 800 meter buffer in 2006 (Urban Atlas)
**Variable name**: physenv_ua_bf_greenurban800_06
**Variable description**:  Total amount of m2 of green urban areas within 800 meter buffer in 2006 from Urban Atlas data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```


### **Variable label**: Total amount of m2 of green urban areas within 800 meter buffer in 2012 (Urban Atlas)
**Variable name**: physenv_ua_bf_greenurban800_12
**Variable description**:  Total amount of m2 of green urban areas within 800 meter buffer in 2012 from Urban Atlas data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```


### **Variable label**: Total amount of m2 of forests within 800 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_forests800_06  
**Variable description**:  Total amount of m2 of forests within 800 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of forests within 800 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_forests800_12  
**Variable description**:  Total amount of m2 of forests within 800 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue space within 800 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_bluespace800_06  
**Variable description**: Total amount of m2 of blue space within 800 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue space within 800 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_bluespace800_12  
**Variable description**: Total amount of m2 of blue space within 800 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of agricultural land within 800 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_agriland800_06  
**Variable description**:  Total amount of m2 of agricultural land within 800 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of agricultural land within 800 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_agriland800_12  
**Variable description**:  Total amount of m2 of agricultural land within 800 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green spaces within 800 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalgreen800_06  
**Variable description**:  Total amount of m2 of green spaces within 800 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green spaces within 800 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalgreen800_12  
**Variable description**:  Total amount of m2 of green spaces within 800 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue spaces within 800 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalblue800_06  
**Variable description**:  Total amount of m2 of blue spaces within 800 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue spaces within 800 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalblue800_12  
**Variable description**:  Total amount of m2 of blue spaces within 800 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue and green spaces within 800 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalbluegreen800_06  
**Variable description**: Total amount of m2 of blue and green spaces within 800 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue and green spaces within 800 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_totalbluegreen800_12  
**Variable description**: Total amount of m2 of blue and green spaces within 800 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green urban areas within 800 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban800_90  
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green urban areas within 800 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban800_00  
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green urban areas within 800 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban800_06  
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green urban areas within 800 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_greenurban800_12  
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of forests within 800 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_forests800_90   
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer in 1990 from CORINE data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of forests within 800 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_forests800_00   
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer in 2000 from CORINE data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Total amount of m2 of forests within 800 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_forests800_06   
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer in 2006 from CORINE data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Total amount of m2 of forests within 800 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_forests800_12   
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer in 2012 from CORINE data.
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue space within 800 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace800_90  
**Variable description**: Total amount of m2 of blue space within 800 meter buffer in 1990 from CORINE data. 
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue space within 800 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace800_00  
**Variable description**: Total amount of m2 of blue space within 800 meter buffer in 2000 from CORINE data. 
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue space within 800 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace800_06  
**Variable description**: Total amount of m2 of blue space within 800 meter buffer in 2006 from CORINE data. 
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue space within 800 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_bluespace800_12  
**Variable description**: Total amount of m2 of blue space within 800 meter buffer in 2012 from CORINE data. 
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of agricultural land within 800 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_agriland800_90  
**Variable description**: Total amount of m2 of agricultural land within 800 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of agricultural land within 800 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_agriland800_00  
**Variable description**: Total amount of m2 of agricultural land within 800 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of agricultural land within 800 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_agriland800_06  
**Variable description**: Total amount of m2 of agricultural land within 800 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of agricultural land within 800 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_agriland800_12  
**Variable description**: Total amount of m2 of agricultural land within 800 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green spaces within 800 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_totalgreen800_90  
**Variable description**: Total amount of m2 of green spaces within 800 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green spaces within 800 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_totalgreen800_00  
**Variable description**: Total amount of m2 of green spaces within 800 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green spaces within 800 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_totalgreen800_06  
**Variable description**: Total amount of m2 of green spaces within 800 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of green spaces within 800 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_totalgreen800_12  
**Variable description**: Total amount of m2 of green spaces within 800 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue spaces within 800 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue800_90  
**Variable description**: Total amount of m2 of blue spaces within 800 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue spaces within 800 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue800_00  
**Variable description**: Total amount of m2 of blue spaces within 800 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue spaces within 800 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue800_06  
**Variable description**: Total amount of m2 of blue spaces within 800 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue spaces within 800 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_totalblue800_12  
**Variable description**: Total amount of m2 of blue spaces within 800 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue and green spaces within 800 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_totalbluegreen800_90  
**Variable description**:  Total amount of m2 of blue and green spaces within 800 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue and green spaces within 800 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_totalbluegreen800_00  
**Variable description**:  Total amount of m2 of blue and green spaces within 800 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue and green spaces within 800 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_totalbluegreen800_06  
**Variable description**:  Total amount of m2 of blue and green spaces within 800 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of blue and green spaces within 800 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_totalbluegreen800_12  
**Variable description**:  Total amount of m2 of blue and green spaces within 800 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 2006 (Urban Atlas)  
**Variable name**: physenv_ua_bf_facilities800_06  
**Variable description**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 2006 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 2012 (Urban Atlas)  
**Variable name**: physenv_ua_bf_facilities800_12  
**Variable description**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 1990 (CORINE)  
**Variable name**: physenv_cn_bf_facilities800_90  
**Variable description**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 1990 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 2000 (CORINE)  
**Variable name**: physenv_cn_bf_facilities800_00  
**Variable description**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 2000 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 2006 (CORINE)  
**Variable name**: physenv_cn_bf_facilities800_06  
**Variable description**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 2006 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 


### **Variable label**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 2012 (CORINE)  
**Variable name**: physenv_cn_bf_facilities800_12  
**Variable description**: Total amount of m2 of sports & leisure facilities within 800 meter buffer in 2012 from CORINE data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 


### **Variable label**: 
**Variable name**: 
**Variable description**:  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: 
**Variable name**: 
**Variable description**:  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



