---
title: "Physical environmental (i.e. geospatial) DataSchema"
output: html_document
---
# Table of Contents
1. [Natural environment - Urban Atlas subdomain] #(Natural-environment - Urban-Atlas-subdomain)  
2. [Natural environment - CORINE subdomain] #(Natural-environment - CORINE-subdomain)  
3. [Built environment - Urban Atlas subdomain] #(Built-environment - Urban-Atlas-subdomain)  
4. [Built environment - CORINE subdomain] #(Built-environment - CORINE-subdomain)  
5. [Land use - Urban Atlas subdomain] #(Land-use - Urban-Atla-subdomain)  
6. [Land use - CORINE subdomain] #(Land-use - CORINE-subdomain)  
7. [Built environment - Urban Atlas subdomain] #(Built-environment - Urban-Atlas-subdomain)  

# Natural environment - Urban Atlas  

### **Variable label**: Distance to green urban areas in 2006 (Urban Atlas)   
**Variable name**: physenv_ua_ne_greenurban_06  
**Variable description**: Absolute distance to the nearest polygon marked as green urban area in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```


### **Variable label**: Distance to green urban areas in 2012 (Urban Atlas)
**Variable name**: physenv_ua_ne_greenurban_12  
**Variable description**: Absolute distance to the nearest polygon marked as green urban area in 2012 from Urban Atlas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Distance to forests in 2006  
**Variable name**: physenv_ua_ne_forests_06  
**Variable description**: Absolute distance to the nearest polygon marked as forest in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Distance to forests in 2012  
**Variable name**: physenv_ua_ne_forests_12
**Variable description**: Absolute distance to the nearest polygon marked as forest in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Distance to blue spaces_2006  
**Variable name**: physenv_ua_ne_bluespace_06  
**Variable description**: Absolute distance to the nearest polygon marked as water in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: - 

**Harmonization status**:
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```
### **Variable label**: Distance to blue spaces_2012  
**Variable name**: physenv_ua_ne_bluespace_12  
**Variable description**: Absolute distance to the nearest polygon marked as water in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: - 

**Harmonization status**:
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Distance to agricultural land_2006  
**Variable name**: physenv_ua_ne_agriland_06  
**Variable description**: Absolute distance to the nearest polygon. No distinction is made between different types of agricultural land in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: - 

**Harmonization comment**:  
**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  
 
```


### **Variable label**: Distance to agricultural land_2012  
**Variable name**: physenv_ua_ne_agriland_12  
**Variable description**: Absolute distance to the nearest polygon. No distinction is made between different types of agricultural land in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: - 

**Harmonization comment**:  
**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written
 
```


### **Variable label**: Distance to total green spaces_2006  
**Variable name**: physenv_ua_ne_totalgreen_06  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of green spaces (forests + green urban  areas) in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Distance to total green spaces_2012  
**Variable name**: physenv_ua_ne_totalgreen_12  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of green spaces (forests + green urban  areas) in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Distance to total blue spaces_2006  
**Variable name**: physenv_ua_ne_totalblue_06  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of blue spaces (water + wetlands) in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Distance to total blue spaces_2012  
**Variable name**: physenv_ua_ne_totalblue_12  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of blue spaces (water + wetlands) in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Distance to total blue and green Spaces_2006  
**Variable name**: physenv_ua_ne_totalbluegreen_06  
**Variable description**: Absolute distance to the nearest polygon. Total of both green and blue space totals in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 

```

### **Variable label**: Distance to total blue and green Spaces_2012  
**Variable name**: physenv_ua_ne_totalbluegreen_12  
**Variable description**: Absolute distance to the nearest polygon. Total of both green and blue space totals in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 

```


### **Variable label**: Area size of green urban areas_2006  
**Variable name**: physenv_ua_ne_greenurban_area_06  
**Variable description**: Area size of the nearest polygon marked as green urban area in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 

```


### **Variable label**: Area size of green urban areas _2012  
**Variable name**: physenv_ua_ne_greenurban_area_12  
**Variable description**: Area size of the nearest polygon marked as green urban area in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Area size of Forests_2006  
**Variable name**: physenv_ua_ne_forests_area_06  
**Variable description**: Area size of the nearest polygon marked as forest in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Area size of Forests_2012  
**Variable name**: physenv_ua_ne_forests_area_12   
**Variable description**: Area size of the nearest polygon marked as forest in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Area size blue spaces area size_2006  
**Variable name**: physenv_ua_ne_bluespace_area_06  
**Variable description**: Area size of the nearest polygon marked as water in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 

```


### **Variable label**: Area size blue spaces area size_2012  
**Variable name**: physenv_ua_ne_bluespace_area_12  
**Variable description**: Area size of the nearest polygon marked as water in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 

```


### **Variable label**: Area size agricultural land_2006  
**Variable name**: physenv_ua_ne_agriland_area_06  
**Variable description**: Area size of the nearest polygon. No distinction is made between different types of agricultural land in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 

```


### **Variable label**: Area size agricultural land_2012  
**Variable name**: physenv_ua_ne_agriland_area_12  
**Variable description**: Area size of the nearest polygon. No distinction is made between different types of agricultural land in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 

```


### **Variable label**: Area size total green spaces_2006  
**Variable name**: physenv_ua_ne_totalgreen_area_06  
**Variable description**: Area size of the nearest polygon. Total of all categories of green spaces (forests + green urban areas) in 2006 from Urban Atalas data.  
**Variable type**: decimal   
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 

```


### **Variable label**: Area size total green spaces_2012  
**Variable name**: physenv_ua_ne_totalgreen_area_12  
**Variable description**: Area size of the nearest polygon. Total of all categories of green spaces (forests + green urban areas) in 2012 from Urban Atalas data.  
**Variable type**: decimal   
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 

```


### **Variable label**: Area size total blue spaces_2006  
**Variable name**: physenv_ua_ne_totalblue_area_06  
**Variable description**: Area size of the nearest polygon. Total of all categories of blue spaces (water + wetlands) in 2006 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written

```


### **Variable label**: Area size total blue spaces_2012  
**Variable name**: physenv_ua_ne_totalblue_area_12  
**Variable description**: Area size of the nearest polygon. Total of all categories of blue spaces (water + wetlands) in 2012 from Urban Atalas data.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written

```


### **Variable label**: Area size total blue and green Spaces_2006  
**Variable name**: physenv_ua_ne_totalbluegreen_area_06  
**Variable description**: Area size of the nearest polygon. Total of both green and blue space totals in 2006 from Urban Atalas data.    
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Area size total blue and green Spaces_2012  
**Variable name**: physenv_ua_ne_totalbluegreen_area_12  
**Variable description**: Area size of the nearest polygon. Total of both green and blue space totals in 2012 from Urban Atalas data.    
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```
### **Variable label**: Green urban areas within 100 meter buffer_0  
**Variable name**: physenv_ua_bf_greenurban100  
**Variable description**: Total amount of m2 of green urban areas within 100 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```

### **Variable label**: Green urban areas within 100 meter buffer_1  
**Variable name**: physenv_ua_bf_greenurban100  
**Variable description**: Total amount of m2 of green urban areas within 100 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```

### **Variable label**: Green urban areas within 400 meter buffer_0  
**Variable name**: physenv_ua_bf_greenurban400  
**Variable description**: Total amount of m2 of green urban areas within 400 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written

```

### **Variable label**: Green urban areas within 400 meter buffer_1  
**Variable name**: physenv_ua_bf_greenurban400  
**Variable description**: Total amount of m2 of green urban areas within 400 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```

### **Variable label**: Green urban areas within 800 meter buffer_0  
**Variable name**: physenv_ua_bf_greenurban800  
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written

```

### **Variable label**: Green urban areas within 800 meter buffer_1  
**Variable name**: physenv_ua_bf_greenurban800  
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written

```

### **Variable label**: Green urban areas within 1000 meter buffer_0  
**Variable name**: physenv_ua_bf_greenurban1000
**Variable description**: Total amount of m2 of green urban areas within 1000 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written

```

### **Variable label**: Green urban areas within 1000 meter buffer_1  
**Variable name**: physenv_ua_bf_greenurban1000
**Variable description**: Total amount of m2 of green urban areas within 1000 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written

```

### **Variable label**: 
**Variable name**: 
**Variable description**: 
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written

```
