---
title: "Physical environmental (i.e. geospatial) DataSchema"
output: html_document
---

# Table of Contents
1. [Natural environment - CORINE - without a buffer](#Natural-environment - CORINE - without a buffer)    
2. [Built environment - CORINE - without a buffer](#Built-environment - CORINE - without a buffer)  
3. [Natural- & Built-environment - CORINE - within a 100m buffer](#Natural- & Built-environment - CORINE - within a 100m buffer)  
4. [Natural- & Built-environment - CORINE - within a 400m buffer](#Natural- & Built-environment - CORINE - within a 400m buffer)  
5. [Natural- & Built-environment - CORINE - within a 800m buffer](#Natural- & Built-environment - CORINE - within a 800m buffer)  
6. [Natural- & Built-environment - CORINE - within a 1000m buffer](#Natural- & Built-environment - CORINE - within a 1000m buffer)  
7. [Natural- & Built-environment - CORINE - within a 1600m buffer](#Natural- & Built-environment - CORINE - within a 1600m buffer)  
8. [Natural- & Built-environment - CORINE - within a 3000m buffer](#Natural- & Built-environment - CORINE - within a 3000m buffer)  
9. [Land-use - CORINE - within a 100m buffer](#Land-use - CORINE - within a 100m buffer)  
10. [Land-use - CORINE - within a 400m buffer](#Land-use - CORINE - within a 400m buffer)  
11. [Land-use - CORINE - within a 800m buffer](#Land-use - CORINE - within a 800m buffer)  
12. [Land-use - CORINE - within a 1000m buffer](#Land-use - CORINE - within a 1000m buffer)  
13. [Land-use - CORINE - within a 1600m buffer](#Land-use - CORINE - within a 1600m buffer)  
14. [Built-environment - Urban-Atlas - urbanicity](#Built-environment - Urban-Atlas - urbanicity)  



**Variable**                | **definition of variable**
----------------------------|---------------------------------------------------
total blue space            | Total of all categories of blue spaces (water + wetlands).  
total green spaces          | Total of all categories of green spaces (forests + green urban areas).  
total blue and green spaces | Total of both green and blue space (forests, green urban areas, water, wetlands).  
Land use mix                | Mix consists of the following categories:
                                                        1. Built-up areas
                                                        2. Industrial & Commercial
                                                        3. Infrastructure
                                                        4. Ports
                                                        5. Green urban areas
                                                        6. Sports & leisure facilities
                                                        7. Agricultural areas
                                                        8. Other natural areas
                                                        9. Blue spaces
                                                        10. Other  


# Please use the following link for other and more detailed information about the CORINE variables:
https://land.copernicus.eu/user-corner/technical-library/Nomenclature.pdf  [23.10.2018]


# Natural environment - CORINE - without a buffer  

### **Variable label**: Distance to green urban areas (CORINE)  
**Variable name**: physenv_cn_ne_grurb_2  
**Variable description**: Absolute distance to the nearest polygon marked as green urban areas from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Distance to forest (CORINE)  
**Variable name**: physenv_cn_ne_forest_2  
**Variable description**: Absolute distance to the nearest polygon marked as forest from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Distance to water (CORINE)  
**Variable name**: physenv_cn_ne_water_2  
**Variable description**: Absolute distance to the nearest polygon marked as water from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Distance to agricultural land (CORINE)  
**Variable name**: physenv_cn_ne_agri_2  
**Variable description**: Absolute distance to the nearest polygon. No distinction is made between different types of agricultural land from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Distance to total green spaces (forests + green urban areas) (CORINE)  
**Variable name**: physenv_cn_ne_ttgr_2  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of green spaces (forests + green urban areas) from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Distance to total blue spaces (water + wetlands) (CORINE)  
**Variable name**: physenv_cn_ne_ttbs_2  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of blue spaces (water + wetlands) from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Distance to total blue and green spaces (water, wetlands, forests, green urban areas) (CORINE)  
**Variable name**: physenv_cn_ne_ttbsgr_2  
**Variable description**: Absolute distance to the nearest polygon. Total of both green and blue spaces (water, wetlands, forests, green urban areas) from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of green urban areas (CORINE)  
**Variable name**: physenv_cn_ne_grurb_as_2  
**Variable description**: Area size of the nearest polygon marked as green urban areas from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of forest (CORINE)  
**Variable name**: physenv_cn_ne_forest_as_2  
**Variable description**: Area size of the nearest polygon marked as forest from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of water (CORINE)  
**Variable name**: physenv_cn_ne_water_as_2  
**Variable description**: Area size of the nearest polygon marked as water from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Area size of agricultural land (CORINE)  
**Variable name**: physenv_cn_ne_agri_as_2  
**Variable description**: Area size of the nearest polygon. No distinction is made between different types of agricultural land from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total green spaces (forests + green urban areas) (CORINE)  
**Variable name**: physenv_cn_ne_ttgr_as_2  
**Variable description**: Area size of the nearest polygon. Total of all categories of green spaces (forests + green urban areas) from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Area size of total blue spaces (water + wetlands) (CORINE)  
**Variable name**: physenv_cn_ne_ttbs_as_2  
**Variable description**: Area size of the nearest polygon. Total of all categories of blue spaces (water + wetlands) from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total blue and green spaces (water, wetlands, forests, green urban areas) (CORINE)  
**Variable name**: physenv_cn_ne_ttbsgr_as_2  
**Variable description**: Area size of the nearest polygon. Total of both green and blue spaces (water, wetlands, forests, green urban areas) from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Distance to facilities (CORINE)  
**Variable name**: physenv_cn_be_facil_2  
**Variable description**: Absolute distance to the nearest polygon marked as sports & leisure facilities from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of facilities (CORINE)  
**Variable name**: physenv_cn_be_facil_as_2  
**Variable description**: Area size of the nearest polygon marked as sports & leisure facilities from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

# Natural- & Built-environment - CORINE - within a 100m buffer  



### **Variable label**: Area size of green urban areas within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_grurb100_2  
**Variable description**: Area size in m² of green urban areas within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**: 

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  

### **Variable label**: Area size of forest within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_forest100_2  
**Variable description**: Area size in m² of forest within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**: 

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of water within 100m buffer 2006 (CORINE)  
**Variable name**: physenv_cn_bf_water100_2  
**Variable description**: Area size in m² of water within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**: 

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of agricultural land within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_agri100_2  
**Variable description**: Area size in m² of agricultural land within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**: 

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total green spaces (forests + green urban areas) within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttgr100_2  
**Variable description**: Area size in m² of total green spaces (forests + green urban areas) within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total blue spaces (water + wetlands) within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttbs100_2  
**Variable description**: Area size in m² of total blue spaces (water + wetlands) within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**: 

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total blue and green spaces (water, wetlands, forests, green urban areas) within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttbsgr100_2  
**Variable description**: Area size in m² of total blue and green spaces (water, wetlands, forests, green urban areas) within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**: 

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


# Natural- & Built-environment - CORINE - within a 400m buffer  

### **Variable label**: Area size of green urban areas within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_grurb400_2  
**Variable description**: Area size in m² of green urban areas within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of forest within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_forest400_2  
**Variable description**: Area size in m² of forest within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  

### **Variable label**: Area size of water within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_water400_2  
**Variable description**: Area size in m² of water within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  



### **Variable label**: Area size of agricultural land within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_agri400_2  
**Variable description**: Area size in m² of agricultural land within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total green spaces (forests + green urban areas) within 400m buffer (CORINE)
**Variable name**: physenv_cn_bf_ttgr400_2  
**Variable description**: Area size in m² of total green spaces (forests + green urban areas) within 400m buffer from CORINE data.
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**: 

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total blue spaces (water + wetlands) within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttbs400_2  
**Variable description**: Area size in m² of total blue spaces (water + wetlands) within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  

### **Variable label**: Area size of total blue and green spaces (water, wetlands, forests, green urban areas) within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttbsgr400_2  
**Variable description**: Area size in m² of total blue and green spaces (water, wetlands, forests, green urban areas) within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  

```  
 

### **Variable label**: Area size of sports & leisure facilities within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_facil400_2  
**Variable description**: Area size in m² of sports & leisure facilities within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

# Natural- & Built-environment - CORINE - within a 800m buffer  


### **Variable label**: Area size of green urban areas within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_grurb800_2  
**Variable description**: Area size in m² of green urban areas within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Area size of m² of forest within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_forest800_2  
**Variable description**: Area size in m² of forest within 800m buffer from CORINE data.
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of water within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_water800_2  
**Variable description**: Area size in m² of water within 800m buffer from CORINE data.
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of agricultural land within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_agri800_2  
**Variable description**: Area size in m² of agricultural land within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Area size of total green spaces (forests + green urban areas) within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttgr800_2  
**Variable description**: Area size in m² of total green spaces (forests + green urban areas) within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total blue spaces (water + wetlands) within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttbs800_2  
**Variable description**: Area size in m² of total blue spaces (water + wetlands) within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Area size of total blue and green spaces (water, wetlands, forests, green urban areas) within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttbsgr800_2  
**Variable description**: Area size in m² of total blue and green spaces (water, wetlands, forests, green urban areas) within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of sports & leisure facilities within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_facil800_2  
**Variable description**: Area size in m² of sports & leisure facilities within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


# Natural- & Built-environment - CORINE - within a 1000m buffer  
 


### **Variable label**: Area size of green urban areas within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_grurb1000_2  
**Variable description**: Area size in m² of green urban areas within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of forest wthin 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_forest1000_2  
**Variable description**: Area size in m² of forest within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Area size of water within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_water1000_2  
**Variable description**: Area size in m² of water within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of agricultural land within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_agri1000_2  
**Variable description**: Area size in m² of agricultural land within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total green spaces (forests + green urban areas) within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttgr1000_2  
**Variable description**: Area size in m² of total green spaces (forests + green urban areas) within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total blue spaces (water + wetlands) within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttbs1000_2  
**Variable description**: Area size in m² of total blue spaces (water + wetlands) within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Area size of total blue and green spaces (water, wetlands, forests, green urban areas) within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttbsgr1000_2  
**Variable description**: Area size in m² of total blue and green spaces (water, wetlands, forests, green urban areas) within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area size of sports & leisure facilities within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_facil1000_2  
**Variable description**: Area size in m² of sports & leisure facilities within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```


### **Variable label**: Area size of green urban areas within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_grurb1600_2  
**Variable description**: Area size in m² of green urban areas within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of forest within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_forest1600_2  
**Variable description**: Area size in m² of forest within 1600m buffer from CORINE data.  

**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of water within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_water1600_2  
**Variable description**: Area size in m² of water within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of agricultural land within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_agri1600_2  
**Variable description**: Area size in m² of agricultural land within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
 


### **Variable label**: Area size of total green spaces (forests + green urban areas) within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttgr1600_2  
**Variable description**: Area size in m² of total green spaces (forests + green urban areas) within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total blue spaces (water + wetlands) within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttbs1600_2  
**Variable description**: Area size in m² of total blue spaces (water + wetlands) within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of total blue and green spaces (water, wetlands, forests, green urban areas) within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_ttbsgr1600_2  
**Variable description**: Area size in m² of total blue and green spaces (water, wetlands, forests, green urban areas) within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of sports & leisure facilities within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_facil1600_2  
**Variable description**: Area size in m² of sports & leisure facilities within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


# Natural- & Built-environment - CORINE - within a 3000m buffer  



### **Variable label**: Area size of sports & leisure facilities within 3000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_facil3000_2  
**Variable description**: Area size in m² of sports & leisure facilities within 3000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```   


# Land-use - CORINE - within a 100m buffer  

### **Variable label**: Land use mix within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu100_2  
**Variable description**: Land use mix in m² within a 100m buffer. It is calculated using an entropy formula from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Area size of built-up area within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu100_bu_2  
**Variable description**: Area size in m² of built-up areas within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of industrial and commercial area within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu100_ic_2  
**Variable description**: Area size in m² of industrial and commercial areas within 100m buffer from CORINE data.
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of infrastructure area within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu100_in_2  
**Variable description**: Area size in m² of infrastructure areas within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Area size of port area within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu100_po_2  
**Variable description**: Area size in m² of ports (airports and sea ports) within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of green urban areas (land use) within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu100_grurb_2  
**Variable description**: Area size in m² of green urban areas (land use) within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```   


### **Variable label**: Area size of sports & leisure facilities area within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu100_facil_2  
**Variable description**: Area size in m² of sports & leisure facilities within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of agricultural land (land use) within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu100_agri_2  
**Variable description**: Area size in m² of agricultural land (land use) within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of other natural areas within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu100_on_2  
**Variable description**: Area size in m² of other natural areas within 100m buffer from CORINE data.
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 


### **Variable label**: Area size of water within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu100_water_2  
**Variable description**: Area size in m² of water within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```   


### **Variable label**: Area size of other areas within 100m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu100_ot_2  
**Variable description**: Area size in m² of other areas within 100m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

# Land-use - CORINE - within a 400m buffer  


### **Variable label**: Land use mix within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu400_2  
**Variable description**: Land use mix in m² within a 400m buffer. It is calculated using an entropy formula from CORINE data. 
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of built-up area within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu400_bu_2  
**Variable description**: Area size in m² of built-up areas within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Area size of industrial and commercial area within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu400_ic_2  
**Variable description**: Area size in m² of industrial and commercial areas within 400m buffer from CORINE data.
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of infrastructure area within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu400_in_2  
**Variable description**: Area size in m² of infrastructure areas within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of port area within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu400_po_2  
**Variable description**: Area size in m² of ports (airports and sea ports) within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of green urban areas (land use) within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu400_grurb_2  
**Variable description**: Area size in m² of green urban areas (land use) within 400m buffer from CORINE data.
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```   


### **Variable label**: Area size of sports & leisure facilities area within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu400_facil_2  
**Variable description**: Area size in m² of sports & leisure facilities within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of agricultural land (land use) within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu400_agri_2  
**Variable description**: Area size in m² of agricultural land (land use) within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of other natural areas within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu400_on_2  
**Variable description**: Area size in m² of other natural areas within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of water within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu400_water_2  
**Variable description**: Area size in m² of water within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of other areas within 400m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu400_ot_2  
**Variable description**: Area size in m² of other areas within 400m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


# Land-use - CORINE - within a 800m buffer  


### **Variable label**: Land use mix within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu800_2  
**Variable description**: Land use mix in m² within a 800m buffer. It is calculated using an entropy formula from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of built-up area within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu800_bu_2  
**Variable description**: Area size in m² of built-up areas within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of industrial and commercial area within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu800_ic_2  
**Variable description**: Area size in m² of industrial and commercial areas within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of infrastructure area within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu800_in_2  
**Variable description**: Area size in m² of infrastructure areas within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of port area within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu800_po_2  
**Variable description**: Area size in m² of ports (airports and sea ports) within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of green urban areas (land use) within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu800_grurb_2  
**Variable description**: Area size in m² of green urban areas (land use) within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Area size of sports & leisure facilities area within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu800_facil_2  
**Variable description**: Area size in m² of sports & leisure facilities within 800m buffer from CORINE data.
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of agricultural land (land use) within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu800_agri_2  
**Variable description**: Area size in m² of agricultural land (land use) within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of other natural areas within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu800_on_2  
**Variable description**: Area size in m² of other natural areas within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of water within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu800_water_2  
**Variable description**: Area size in m² of water within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of other areas within 800m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu800_ot_2  
**Variable description**: Area size in m² of other areas within 800m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


# Land-use - CORINE - within a 1000m buffer  

### **Variable label**: Land use mix within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1000_2  
**Variable description**: Land use mix in m² within a 1000m buffer. It is calculated using an entropy formula from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of built-up area within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1000_bu_2  
**Variable description**: Area size in m² of built-up areas within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of industrial and commercial area within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1000_ic_2  
**Variable description**: Area size in m² of industrial and commercial areas within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of infrastructure areas within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1000_in_2  
**Variable description**: Area size in m² of infrastructure areas within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of port area within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1000_po_2  
**Variable description**: Area size in m² of ports (airports and sea ports) within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of green urban areas (land use) within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1000_grurb_2  
**Variable description**: Area size in m² of green urban areas (land use) within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Area size of sports & leisure facilities areas within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1000_facil_2  
**Variable description**: Area size in m² of sports & leisure facilities within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of agricultural land (land use) within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1000_agri_2  
**Variable description**: Area size in m² of agricultural land (land use) within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Area size of other natural areas within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1000_on_2  
**Variable description**: Area size in m² of other natural areas within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of water within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1000_water_2  
**Variable description**: Area size in m² of water within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Area size of other areas within 1000m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1000_ot_2  
**Variable description**: Area size in m² of other areas within 1000m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

# Land-use - CORINE - within a 1600m buffer  



### **Variable label**: Land use mix within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1600_2  
**Variable description**: Land use mix in m² within a 1600m buffer. It is calculated using an entropy formula from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of built-up areas within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1600_bu_2  
**Variable description**: Area size in m² of built-up areas within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Area size of industrial and commercial areas within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1600_ic_2  
**Variable description**: Area size in m² of industrial and commercial areas within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of infrastructure areas within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1600_in_2  
**Variable description**: Area size in m² of infrastructure areas within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of port area within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1600_po_2  
**Variable description**: Area size in m² of ports (airports and sea ports) within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Area size of green urban areas (land use) within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1600_grurb_2  
**Variable description**: Area size in m² of green urban areas (land use) within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of sports & leisure facilities areas within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1600_facil_2  
**Variable description**: Area size in m² of sports & leisure facilities within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of agricultural land (land use) within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1600_agri_2  
**Variable description**: Area size in m² of agricultural land (land use) within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Area size of other natural areas within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1600_on_2  
**Variable description**: Area size in m² of other natural areas within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Area size of water within 1600m buffer (CORINE)  
**Variable name**: physenv_cn_bf_lu1600_water_2  
**Variable description**: Area size in m² of water within 1600m buffer from CORINE data.  
**Variable type**: decimal  
**Variable unit**: m²  
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


# Built-environment - Urban-Atlas - urbanicity


### **Variable label**: Urbanicity grade (CORINE)  
**Variable name**: physenv_cn_urbcy_2  
**Variable description**: Urbanicity grade based on the classes from the CORINE. This is a categorical variable with 2 classes being from continuous urban to dense, medium, low, and very low density from CORINE data.  
**Variable type**: integer  
**Variable unit**:   
**Category coding**:  


**physenv_cn_urbcy_90** | **Urbanicity grade (CORINE)**
------------------------| --------------------------------------------------
0 | Continuous urban fabric (S.L. > 80%)  
1 | Discontinuous urban fabric (S.L.: 30% - 80%)  

**Harmonization status**:  
**Harmonization comment**: CORINE Data 2006  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

