---
title: "Physical environmental (i.e. geospatial) DataSchema"
output: html_document
---
# Table of Contents
1. [Natural environment - Urban Atlas subdomain] #(Natural-environment - Urban-Atlas-subdomain)  
2. [Natural environment - CORINE subdomain] #(Natural-environment - CORINE-subdomain)  
3. [Built environment - Urban Atlas subdomain] #(Built-environment - Urban-Atlas-subdomain)  
4. [Built environment - CORINE subdomain] #(Built-environment - CORINE-subdomain)  
5. [Land use - Urban Atlas subdomain] #(Land-use - Urban-Atla-subdomain)  
6. [Land use - CORINE subdomain] #(Land-use - CORINE-subdomain)  
7. [Built environment - Urban Atlas subdomain] #(Built-environment - Urban-Atlas-subdomain)  

# Natural environment - Urban Atlas  

### **Variable label**: Distance to green urban areas_0   
**Variable name**: physenv_ua_ne_greenurban  
**Variable description**: Absolute distance to the nearest polygon marked as green urban area  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written  


### **Variable label**: Distance to green urban areas_1 
**Variable name**: physenv_ua_ne_greenurban  
**Variable description**: Absolute distance to the nearest polygon marked as green urban area  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Forests_0    
**Variable description**: Absolute distance to the nearest polygon marked as forest.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Forests_1  
**Variable description**: Absolute distance to the nearest polygon marked as forest.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE} 


### **Variable label**: Blue spaces_0 
**Variable name**: physenv_ua_ne_bluespace  
**Variable description**: Absolute distance to the nearest polygon marked as water.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: - 

**Harmonization status**:
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Blue spaces_1
**Variable name**: physenv_ua_ne_bluespace  
**Variable description**: Absolute distance to the nearest polygon marked as water.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: - 

**Harmonization status**:
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Agricultural land_0  
**Variable name**: physenv_ua_ne_agriland  
**Variable description**: Absolute distance to the nearest polygon. No distinction is made between different types of agricultural land.
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: - 

**Harmonization comment**:  
**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written
 
  
### **Variable label**: Agricultural land_1  
**Variable name**: physenv_ua_ne_agriland 
**Variable description**: Absolute distance to the nearest polygon. No distinction is made between different types of agricultural land. **Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Total green spaces_0   
**Variable name**: physenv_ua_ne_totalgreen  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of green spaces (forests + green urban  areas).  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Total green spaces_1   
**Variable name**: physenv_ua_ne_totalgreen  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of green spaces (forests + green urban  areas).  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Total blue spaces_0  
**Variable name**: physenv_ua_ne_totalblue  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of blue spaces (water + wetlands).  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Total blue spaces_1  
**Variable name**: physenv_ua_ne_totalblue  
**Variable description**: Absolute distance to the nearest polygon. Total of all categories of blue spaces (water + wetlands).  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Total blue and green Spaces_0  
**Variable name**: physenv_ua_ne_totalbluegreen  
**Variable description**: Absolute distance to the nearest polygon. Total of both green and blue space totals.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Total blue and green Spaces_1  
**Variable name**: physenv_ua_ne_totalbluegreen  
**Variable description**: Absolute distance to the nearest polygon. Total of both green and blue space totals.  
**Variable type**: decimal  
**Variable unit**: meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Green urban areas area size_0  
**Variable name**: physenv_ua_ne_greenurban_area  
**Variable description**: Area size of the nearest polygon marked as green urban area  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Green urban areas area size_1  
**Variable name**: physenv_ua_ne_greenurban_area  
**Variable description**: Area size of the nearest polygon marked as green urban area  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Forests area size_0  
**Variable name**:physenv_ua_ne_forests_area  
**Variable description**: Area size of the nearest polygon marked as forest.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Forests area size_1  
**Variable name**:physenv_ua_ne_forests_area  
**Variable description**: Area size of the nearest polygon marked as forest.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Blue spaces area size_0  
**Variable name**: physenv_ua_ne_bluespace_area  
**Variable description**: Area size of the nearest polygon marked as water.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Blue spaces area size_0  
**Variable name**: physenv_ua_ne_bluespace_area  
**Variable description**: Area size of the nearest polygon marked as water.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Agricultural land area size_0  
**Variable name**: physenv_ua_ne_agriland_area  
**Variable description**: Area size of the nearest polygon. No distinction is made between different types of agricultural land.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Agricultural land area size_1  
**Variable name**: physenv_ua_ne_agriland_area  
**Variable description**: Area size of the nearest polygon. No distinction is made between different types of agricultural land.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Total green spaces area size_0    
**Variable name**: physenv_ua_ne_totalgreen_area  
**Variable description**: Area size of the nearest polygon. Total of all categories of green spaces (forests + green urban areas).   
**Variable type**: decimal   
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Total green spaces area size_1    
**Variable name**: physenv_ua_ne_totalgreen_area  
**Variable description**: Area size of the nearest polygon. Total of all categories of green spaces (forests + green urban areas).   
**Variable type**: decimal   
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written 


### **Variable label**: Total blue spaces area size_0  
**Variable name**: physenv_ua_ne_totalblue_area  
**Variable description**: Area size of the nearest polygon. Total of all categories of blue spaces (water + wetlands).  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written


### **Variable label**: Total blue spaces area size_1  
**Variable name**: physenv_ua_ne_totalblue_area  
**Variable description**: Area size of the nearest polygon. Total of all categories of blue spaces (water + wetlands).  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written


### **Variable label**: Total blue and green Spaces area size_0  
**Variable name**: physenv_ua_ne_totalbluegreen_area  
**Variable description**: Area size of the nearest polygon. Total of both green and blue space totals.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Total blue and green Spaces area size_1  
**Variable name**: physenv_ua_ne_totalbluegreen_area  
**Variable description**: Area size of the nearest polygon. Total of both green and blue space totals.  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Green urban areas within 100 meter buffer_0  
**Variable name**: physenv_ua_bf_greenurban100  
**Variable description**: Total amount of m2 of green urban areas within 100 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Green urban areas within 100 meter buffer_1  
**Variable name**: physenv_ua_bf_greenurban100  
**Variable description**: Total amount of m2 of green urban areas within 100 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Green urban areas within 400 meter buffer_0  
**Variable name**: physenv_ua_bf_greenurban400  
**Variable description**: Total amount of m2 of green urban areas within 400 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written


### **Variable label**: Green urban areas within 400 meter buffer_1  
**Variable name**: physenv_ua_bf_greenurban400  
**Variable description**: Total amount of m2 of green urban areas within 400 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -  

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  


### **Variable label**: Green urban areas within 800 meter buffer_0  
**Variable name**: physenv_ua_bf_greenurban800  
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written


### **Variable label**: Green urban areas within 800 meter buffer_1  
**Variable name**: physenv_ua_bf_greenurban800  
**Variable description**: Total amount of m2 of green urban areas within 800 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written


### **Variable label**: Green urban areas within 1000 meter buffer_0  
**Variable name**: physenv_ua_bf_greenurban1000
**Variable description**: Total amount of m2 of green urban areas within 1000 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written

### **Variable label**: Green urban areas within 1000 meter buffer_1  
**Variable name**: physenv_ua_bf_greenurban1000
**Variable description**: Total amount of m2 of green urban areas within 1000 meter buffer  
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written

### **Variable label**: 
**Variable name**: 
**Variable description**: 
**Variable type**: decimal  
**Variable unit**: square meters  
**Category coding**: -

**Harmonization comment**:  
```{r, echo=TRUE}  
#This is where the R-script will be written

